Verifying Demonstrations

### 2020-06-03 paper/performance.tex
Adds a table summarizing the performance

We will now review the performance of the proposed protocols.
Since the construction is designed as a drop-in replacement for the Schnorr 
identification-scheme~\cite{Schnorr} as \iac{ZKPK} protocol, we will focus on 
how much we must \enquote{pay} for the \ac{DB} property.

>>>>

\mode<presentation>{%
  \begin{frame}
    \begin{question}
      \begin{itemize}
        \item How costly is this compared to non-\acs{DB} Schnorr?
      \end{itemize}
    \end{question}
  \end{frame}
}

We will now review the performance of the proposed protocols.
Since the construction is designed as a drop-in replacement for the Schnorr 
identification-scheme~\cite{Schnorr} as \iac{ZKPK} protocol, we will focus on 
how much we must \enquote{pay} for the \ac{DB} property.
We summarize the results in \cref{performance-overview}.

\begin{frame}
  \begin{table}
    \caption{%
      A summary of how costly \acl*{DB} is in terms of performance.
      \(m, l\in \mathcal{O}(\log \lambda)\).
    }\label{performance-overview}
    \begin{tabular}{lrrrr}
      \toprule
      Protocol
      & Rand.
      & Arith.
      & Exp.
      & Pairings\\
      \midrule
      Schnorr             & \(l\)             & 3    & 3      & 0\\
      DB, mutual          & \(ml\)            & 3m   & 3      & 0\\
      DB, \acs*{PKI} \(\sum\)
                          & \(8\lambda + ml\)
                          & \(10m+8\)
                          & \(25\)
                          & \(14\)\\
      ---\acs*{DHKE}      & \(\lambda\)       & 0    & 4      & 0\\
      ---CL04 blind       & \(2\lambda\)      & 0    & 5      & 8\\
      ---DB               & \(5\lambda + ml\)    & \(10m + 2\) & 6 & 0\\
      ---Verification     & 0    & 6 & 10 & 6\\
      \bottomrule
    \end{tabular}
  \end{table}
\end{frame}
